---
title: "Aides Drug"
author: "Kelly Douglas"
date: "Fall 2019"
output: html_document
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
avast <-read.csv(file="avastivironal.csv",header=TRUE)
avastf <- filter(avast,sex=="gal")
```

# Introduction

For this test I will be seeing if the new drug for aides is affected based on if you are a female. Are more females getting Aides with the drug or not? 
$H_0$: There is no correlation between a person being a female and them having the medication work to not get Aids.
$H_A$: If a person is a female then the drug will not work for them.



A new  preventative aides (abacavirinol) is under test in clinical trials. Analyze the effectiveness of this drug across the board. Consider population subgroups by gender, drug use, and sexual orientation. Finish this!

# Methods
For this question I will be using the barchart and chisq test and the fisher test to decide if there is a correlation between being a female and if the new Aides drug works. 


#Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results
```{r}
barchartGC(~infected+treatment,data=avastf,type="percent")
barchartGC(~infected+treatment,data = avastf)
```
Based on the data above there is a smaller percent of females that got Aides taking the drug than those that took the placebo. The drug is effective since less females contracted aides that took the drug than those that took the placebo. 


### Numerical Descriptive Results

```{r}
table1 <- xtabs(~infected+treatment,data=avastf)
rowPerc(table1)
colPerc(table1)
```
Based on the data above less females got the disease that took the drug than those that took the placebo. So the drug is effective for females. 


## Inferential Results
```{r}
chisq.test(table1)
chisqtestGC(table1)
fisher.test(table1)
```
Based on the information above the p-value is very small. It shows that the drug is effective for females. It shows that the amount that contracted aids taking the drug was smaller than those that contracted aids taking the placebo. 
<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->


# Discussion and Conclusion
This drug is effective for females. Based on the p-value I reject the null hypothesis. It is an effective drug. 
<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->
